Rigidity of Expectations: Additional Evidence from Density Forecasts of the Inflation by Professionals and Households

### 2019-10-17 paper/Draft.tex
NLP tasks put all articles info in a dataframe
Corrected disagreement fomula for NI model in the draft. But codes on estimation from simulated data remains debugging.

	This paper is related to four strands of literature. First, it is realted to a series of empirical work directly testing and evaluating the various theories on expectations theories using survey data. For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}. More recent examples include \citet{coibion2018firms} on firms' managers. In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demographics, cognitive abilities and macroeconomic histories experienced(\citet{malmendier2015learning}, \citet{das2017socioeconomic} and \citet{d2019iq}, etc.). In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}.  However, all of these studies simply rely upon point forecasts instead of density forecast or surveyed uncertainty. This is one theme on which this paper differs from the existing literature.

@@

	NI also predicts non-zero disagreement in the presence of private signals. The behavior of disagreement across agents come from the difference in realized private signals. Specifically, it is equal to the following.

	\begin{eqnarray}
		\begin{aligned}
			\overline {Disg}_{t+h|t} = \rho^{2h} P^2_\xi \sigma^2_\xi  
		\end{aligned}
	\end{eqnarray}

	The implications for disagreement are straightforward. First, the disagreement decrease with the forecast horizon due to discounting. Second, the disagreement depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$. Third, similar to SE, the disagreements also increase with the rigidity parameter $P$ in this model.

>>>>

	This paper is related to four strands of literature. First, it is realted to a series of empirical work directly testing and evaluating  various theories on expectations formation using survey data. For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}. More recent examples include \citet{coibion2018firms} on firms' managers. In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demographics, cognitive abilities and macroeconomic histories experienced(\citet{malmendier2015learning}, \citet{das2017socioeconomic} and \citet{d2019iq}, etc.). In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}.  However, all of these studies simply rely upon point forecasts instead of density forecast or surveyed uncertainty. This is one theme on which this paper differs from the existing literature.

@@

	NI also predicts non-zero disagreement in the presence of private signals. The behavior of disagreement across agents come from the difference in the entire histories of realized private signals. Specifically, it is equal to the following.

	\begin{eqnarray}
		\begin{aligned}
			\overline {Disg}_{t+h|t} =  (1-PH) \overline {Disg}_{t+h|t-1} + \rho^{2h} P^2_\xi \sigma^2_\xi 
		\end{aligned}
	\end{eqnarray}

	The implications for disagreement are straightforward. First, the serial correlation between disagreement is proportional to the rigidity parameter $(1-PH)$ and, similar to SE, it increases with the rigidity parameter $P$ in this model. Second, the disagreement decrease with the forecast horizon due to discounting. Third, the disagreement depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$.
